---
title: "Debugging and state management"
format: html
---

# Instructions

For your final milestone, you'll create a parameterized Quarto report and write a function to render that report, and then create one report for each disease in a vector.

To learn more about the variables contained in the data set, refer to the data dictionary here: https://rstudio.github.io/academy-pinr-heart-catheterization/assets/heart-catheterization_dictionary.html

# Milestone

## Milestone 6

In this milestone, you'll parameterize the report you made in Milestone 4 so that it will work for any RHC data set. Then, you'll write a function to render the report and iterate to create multiple reports.

## Recreation

### Parameterize

First, parameterize the data set analyzed in `rhc-report.qmd` by:

* Adding a `disease` parameter to the YAML header, so it looks like this:

```
---
title: "Right heart catheterization"
format: 
  html:
    embed-resources: true
execute:
  echo: false
  message: false
  warning: false
params:
  disease: "arf"
---
```

* Editing the line where the specific RHC data set is read in (`rhc <- read_rhc("data/arf.csv")`) to use `params$disease` instead:

```{r}
#| eval: false
rhc <- read_rhc(glue::glue("data/{params$disease}.csv"))
```

These two changes will allow you to use this report for any RHC data set. Try it out by changing `disease: "arf"` to `disease: "cirrhosis"` and then knitting the report. 

### Function

Next, write a function named `rhc_report()` that creates a report based on your parameterized report. Your function should:

* Take one argument: `dx`, a string specifying the disease to use in the report. 
* Use `quarto::quarto_render()` to render `rhc-report.qmd`, setting the parameter `disease` to `dx`.
* Name the output file according to `dx`.

_Hint:_ Here's an example call to `quarto::quarto_render()` that renders a report called `color.qmd` that has a `color` parameter:

```{r}
#| label: color-example
#| eval: false
quarto::quarto_render(
  "color.qmd",
  execute_params = list(color = "blue"),
  output_file = "blue.html"
)
```

Write `rhc_report()` in `heart-catheterization_06_debug.R`.

### Iterate

Next, use `rhc_report()` and a purrr function to create a report for each disease in the following vector:

```{r}
#| label: disease-vec
diseases <- c("arf", "colon_cancer", "copd", "lung_cancer")
```

## Extension

For your extension, expand upon the report in any way that you'd like.

