---
title: "Function-writing best practices"
format: html
---

# Instructions

This week you learned about best practices for function writing, including incorporating validation and stopping into your functions. In this milestone, you'll add validation and stopping conditions to `summarize_diagnosis()`.

To learn more about the variables contained in the data set, refer to the data dictionary here: https://rstudio.github.io/academy-pinr-heart-catheterization/assets/heart-catheterization_dictionary.html

# Milestone

```{r}
#| label: setup
#| include: false
source("heart-catheterization_05_best-practices.R")
# Load your packages here

```

## Milestone 5

In this milestone, you'll add validation and stopping conditions to `summarize_diagnosis()`.

## Recreation

The script `heart-catheterization_05_best-practices.R` contains all the functions you've written so far, including `summarize_diagnosis()`.

We can make `summarize_diagnosis()` more robust by validating arguments and stopping early if necessary.

Check for the following four situations in `summarize_diagnosis()`:

1. Check if `data` is a data frame, and throw an error if it's not. Use the error message "`data` must be a data frame."
2. Check if `diagnosis_data` is a data frame, and throw an error if it's not. Use the error message "`diagnosis_data` must be a data frame."
3. Check if `dx` is a character vector of length one, and throw an error if it's not. Use the error message "`dx` must be a character vector of length 1."
4. Check if `dx` is a diagnosis included in `diagnosis_data` and throw an error if it's not. Use the error message "xyz is not a diagnosis included in `diagnosis_data`." Replace "xyz" with the diagnosis provided by the user.

_Hint:_ You'll need to edit the `summarize_diagnosis()` code so that you can check if `dx` is in the `diagnosis` column after you pivot.

Use the cli package to signal errors. 

When you're done, run the following code chunk to confirm that you're function works as expected.

```{r}
#| label: compare
#| error: true
arf <- read_rhc("data/arf.csv")
diagnosis_data <- read_csv("data/diagnoses.csv")

# Should produce the error message "`data` must be a data frame."
summarize_diagnosis(list(1, 2, 3), diagnosis_data, "liverhx")

# Should produce the error message "`diagnosis_data` must be a data frame."
summarize_diagnosis(arf, list(1, 2, 3), "liverhx")

# Should produce the error message "na is not a diagnosis included in `diagnosis_data`."
summarize_diagnosis(arf, diagnosis_data, "na")

# Should produce the error message "`dx` must be a character vector of length 1."
summarize_diagnosis(arf, diagnosis_data, c("psychhx", "dementhx"))

# Should work successfully
summarize_diagnosis(arf, diagnosis_data, "psychhx")
```


## Extension

Consider updating the other functions in `heart-catheterization_05_best-practices.R` to incorporate argument validation.

