---
title: "Control function flow"
format: html
---

# Instructions

This week, you learned how to work with lists, iterate with purrr, and control function flow with conditional statements. In this milestone, you'll use what you've learned to write a new function and then iterate over a vector of inputs to that function.

To learn more about the variables contained in the data set, refer to the data dictionary here: https://rsacdn.link/milestones/internal/pinr/heart-catheterization/assets/heart-catheterization_dictionary.html

# Milestone

```{r}
#| label: setup
#| include: false
source("heart-catheterization_02_conditionals.R")
# Load your packages here

```

## Milestone 2

In this milestone, you'll write a function that summarizes other diagnoses assigned to patients in the RHC data sets. Then, you'll iterate over a vector to produce multiple of these summary tables at once.

## Recreation

### Part 1 - Summarize diagnoses

First, in the script `heart-catheterization_02_conditionals.R`, create a function named `summarize_diagnosis()`. `summarize_diagnosis()` should take three arguments:

* `data`: A processed RHC data set, like the result of `read_rhc("data/cirrhosis.csv")`.
* `diagnosis_data`: A diagnoses data set, like the one stored in `data/diagnoses.csv`.
* `dx`: A string containing a diagnosis.

Then, `summarize_diagnosis()` should create a summary table displaying the number of patients in `data` with `dx`, like this:

```{r}
#| label: recreate-this
#| echo: false
solution <- readr::read_csv("data/solution_02.csv")
solution
```

Use the following code to help you get started:

```{r}
#| label: get-started
#| eval: false
data |>
  left_join(diagnosis_data, by = "ptid") |>
  pivot_longer(
    cols = cardiohx:amihx,
    names_to = "diagnosis",
    values_to = "present"
  )
```

When you're done, un-comment and run the following code to see if your function works as expected.

```{r}
#| label: compare-1
#| message: false
# cirrhosis <- read_rhc("data/cirrhosis.csv")
# diagnoses <- read_csv("data/diagnoses.csv")
# result <- summarize_diagnosis(cirrhosis, diagnoses, dx = "dementhx")
# waldo::compare(result, solution)
```

### Part 2 - Iterate

Next, use purrr and `summarize_diagnosis()` to create a summary table for each diagnosis in the following vector:

```{r}
#| label: dx-vec
#| eval: false
c("malighx", "renalhx", "cardiohx")
```

Set `data` to `cirrhosis` and `diagnosis_data` to `diagnoses`.

Write your code in `heart-catheterization_02_conditionals.R`.

## Extension

For your extension, consider expanding upon or further developing `summarize_diagnosis()`, or writing a new function.
