---
title: "Iterate and write functions with the tidyverse"
format: html
---

# Instructions

In this milestone, you'll use tidy evaluation to write a function that plots the RHC data sets.

To learn more about the variables contained in the data set, refer to the data dictionary here: https://rsacdn.link/milestones/internal/pinr/heart-catheterization/assets/heart-catheterization_dictionary.html

# Milestone

```{r}
#| label: setup
#| include: false
source("heart-catheterization_03_iterate.R")
# Load your packages here
library(tidyverse)
```

## Milestone 3

In this milestone you'll write a function to plot the RHC data.

## Recreation

The script `heart-catheterization_03_iterate.R` contains all the functions you've written so far. In this script, write a new function named `plot_rhc()` that:

* Takes two arguments: `data` and `var`.
* Plots a boxplot of `var` if `var` is numeric.
* Plots a barplot of `var` if `var` is not numeric. 
* Labels the x-axis "RHC".


Using the File Explorer, navigate to the `images/` directory, then click on `image_03_numeric.png` to open an image. **Your plots should look like this if `var` is numeric.** 


Using the File Explorer, navigate to the `images/` directory, then click on `image_03_categorical.png` to open an image. **Your plot should look like this if `var` is categorical.**

When you're done, run the following code chunk to test your function. Your plots should match the ones displayed above. 

```{r}
#| label: compare
cirrhosis <- read_rhc("data/cirrhosis.csv")
cirrhosis |> plot_rhc(age)
cirrhosis |> plot_rhc(race)
```

_Hint:_ To detect if `var` is numeric or not, first extract `var` from `data`, like this:

```{r}
#| label: hint
#| eval: false
col_var <-
  data |>
  pull({{ var }})
```


## Extension

For your extension, consider writing other functions that plot different aspects of the RHC data sets. 

